Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-07 paper/Paper.tex
update contracts

        //move all reward tokens
        rewardToken[_newContract] += rewardToken[address(this)];
        rewardToken[address(this)] = 0;
    }

>>>>

        //move all reward tokens
        rewardToken[_newContract] += rewardToken[address(this)];
        rewardToken[address(this)] = 0;
        DAOpaidOut[_newContract] += DAOpaidOut[address(this)];
        DAOpaidOut[address(this)] = 0;
    }
